Clicks and Cliques

### 2018-12-23 papersoul.Rnw
tidy import.plot4 chunk

# stat methods
library(randomForest)
library(survey)
library(fpc)
library(reldist)

@@

\begin{figure}
<<import.plot4, dependson='data',echo=FALSE, fig.height=5, fig.width=8,message=FALSE,warning=FALSE,warning=FALSE, fig.keep='all'>>=
library(ggdendro)

xx <- dcast(important[,c('dim','QSB','mdg.pr')], QSB~dim)
rownames(xx) <- xx$QSB
d <- dist( xx[,-1] )
hc <- hclust(d, method='ward')
xx$comu.cl <- as.numeric(cutree(hc,5))

dd.row <- as.dendrogram(hc)
ddata_x <- dendro_data(dd.row)
p2 <- ggplot(segment(ddata_x))+geom_segment(aes(x=x, y=y, xend=xend, yend=yend),extent = "device")
labs <- label(ddata_x)

p2 + geom_text(data=labs, aes(label=label, x=x, y=-1.5))+coord_flip()+scale_y_reverse()+theme(legend.position = 'none',axis.title.x = element_blank(),axis.title.y = element_blank()) + ylim(c(10,-3))

>>>>

# stat methods
library(randomForest)
library(survey)
library(fpc)
library(reldist) 
library(ggdendro)

@@

\begin{figure}
<<import.plot4, dependson='data',echo=FALSE, fig.height=5, fig.width=8,message=FALSE,warning=FALSE,warning=FALSE, fig.keep='all'>>=

xx <- important %>% 
  select(dim, QSB, mdg.pr) %>% 
  spread(dim, mdg.pr)

hc <- xx[,-1]  %>% 
  data.frame() %>% 
  `rownames<-`(xx$QSB) %>%  
  dist( ) %>% 
  hclust( method = 'ward')

xx %<>% mutate(comu.cl = as.numeric(cutree(hc,5)))

ddata_x <- dendro_data(as.dendrogram(hc))

ggplot(segment(ddata_x)) + 
  geom_segment(aes(x = x, y = y, xend = xend, yend = yend),extent = "device") +
  geom_text(data = label(ddata_x), aes(label = label, x = x, y = -1.5)) + 
  coord_flip() + scale_y_reverse() + 
  theme(legend.position = 'none',axis.title.x = element_blank(),axis.title.y = element_blank()) + ylim(c(10,-3))
